---
title: "Emotional Engagement (Eye tracking)"
author: "Nanna, Esther, Alberte og Simon"
date: "19 feb 2018"
output: html_document
---

Preprocessing of data

```{r setup, include=FALSE}

# Set working directory 
setwd("C:/Users/simon/Google Drev/Uni/2018 - Eye tracking")

# Libraries
library(dplyr)
library(stringr)
library(groupdata2)
library(cvms)
library(lmerTest)

# Load datafiles
fix=read.csv("FixationsV1.csv")
sac=read.csv("SaccadesV1.csv")
samp=read.csv("SamplesV1.csv")

# Subset data
fix_vis = subset(fix, Task == "VisualSearch")
fix_soc = subset(fix, Task == "SocialEngagement")

# Adding condition to Visual search
for (i in 1:nrow(fix_vis)){
  if (fix_vis$SearchOrder[i] == "1" & fix_vis$Trial[i] < 6) {
    fix_vis$Condition[i] = "Star"
  }
  if (fix_vis$SearchOrder[i] == "1" & fix_vis$Trial[i] > 5) {
    fix_vis$Condition[i] = "Count"
  }
  if (fix_vis$SearchOrder[i] == "2" & fix_vis$Trial[i] < 6) {
    fix_vis$Condition[i] = "Count"
  }
  if (fix_vis$SearchOrder[i] == "2" & fix_vis$Trial[i] > 5) {
    fix_vis$Condition[i] = "Star"
  }
}

# Adding condition to social engagement
# Load logfiles
folder = "PupilsLogs/"
fileList = list.files(path=folder, pattern="*.csv")
setwd("PupilsLogs")
pupil = do.call(rbind, lapply(fileList, function(x) read.csv(x, stringsAsFactors = F)))
setwd("C:/Users/simon/Google Drev/Uni/2018 - Eye tracking")

pupil$X = NULL

pupil$Trial = list(1, 2, 3, 4, 5, 6, 7, 8)

# Rename columns 
pupil = rename(pupil, "ParticipantID" = "subject")
  
# Merge files
fix_soc=merge(pupil, fix_soc)
  
# To get gender from video
fix_soc$ActorGender = str_extract(fix_soc$video, "\\w{1}")

# To get directness
for (i in 1:nrow(fix_soc)){
  if (grepl("div", fix_soc$video[i])) {
    fix_soc$Directness[i] = "Divergent"}
  if (grepl("dir", fix_soc$video[i])) {
    fix_soc$Directness[i] = "Direct"}
}

# To get ostensiveness
for (i in 1:nrow(fix_soc)){
  if (grepl("+o", fix_soc$video[i])) {
    fix_soc$Ostensiveness[i] = "Yes"}
  if (grepl("-o", fix_soc$video[i])) {
    fix_soc$Ostensiveness[i] = "No"}
}

# Replicate the above code to use on the other files

# Subset data
sac_vis = subset(sac, Task == "VisualSearch")
sac_soc = subset(sac, Task == "SocialEngagement")

# Adding condition to Visual search
for (i in 1:nrow(sac_vis)){
  if (sac_vis$SearchOrder[i] == "1" & sac_vis$Trial[i] < 6) {
    sac_vis$Condition[i] = "Star"
  }
  if (sac_vis$SearchOrder[i] == "1" & sac_vis$Trial[i] > 5) {
    sac_vis$Condition[i] = "Count"
  }
  if (sac_vis$SearchOrder[i] == "2" & sac_vis$Trial[i] < 6) {
    sac_vis$Condition[i] = "Count"
  }
  if (sac_vis$SearchOrder[i] == "2" & sac_vis$Trial[i] > 5) {
    sac_vis$Condition[i] = "Star"
  }
}

# Merge files
sac_soc=merge(pupil, sac_soc)

# To get gender from video
sac_soc$ActorGender = str_extract(sac_soc$video, "\\w{1}")

# To get directness
for (i in 1:nrow(sac_soc)){
  if (grepl("div", sac_soc$video[i])) {
    fix_soc$Directness[i] = "Divergent"}
  if (grepl("dir", sac_soc$video[i])) {
    sac_soc$Directness[i] = "Direct"}
}

# To get ostensiveness
for (i in 1:nrow(sac_soc)){
  if (grepl("+o", sac_soc$video[i])) {
    sac_soc$Ostensiveness[i] = "Yes"}
  if (grepl("-o", sac_soc$video[i])) {
    sac_soc$Ostensiveness[i] = "No"}
}

# To do the same for sample data

# Subset data
samp_vis = subset(samp, Task == "VisualSearch")
samp_soc = subset(samp, Task == "SocialEngagement")

# Adding condition to Visual search
for (i in 1:nrow(samp_vis)){
  if (samp_vis$SearchOrder[i] == "1" & samp_vis$Trial[i] < 6) {
    samp_vis$Condition[i] = "Star"
  }
  if (samp_vis$SearchOrder[i] == "1" & samp_vis$Trial[i] > 5) {
    samp_vis$Condition[i] = "Count"
  }
  if (samp_vis$SearchOrder[i] == "2" & samp_vis$Trial[i] < 6) {
    samp_vis$Condition[i] = "Count"
  }
  if (samp_vis$SearchOrder[i] == "2" & samp_vis$Trial[i] > 5) {
    samp_vis$Condition[i] = "Star"
  }
}

# Merge files
samp_soc=merge(pupil, samp_soc)

# To get gender from video
samp_soc$ActorGender = str_extract(samp_soc$video, "\\w{1}")

# To get directness
for (i in 1:nrow(samp_soc)){
  if (grepl("div", samp_soc$video[i])) {
    fix_soc$Directness[i] = "Divergent"}
  if (grepl("dir", samp_soc$video[i])) {
    samp_soc$Directness[i] = "Direct"}
}

# To get ostensiveness
for (i in 1:nrow(samp_soc)){
  if (grepl("+o", samp_soc$video[i])) {
    samp_soc$Ostensiveness[i] = "Yes"}
  if (grepl("-o", samp_soc$video[i])) {
    samp_soc$Ostensiveness[i] = "No"}
}


```

Analysing the data from the emotional engagement experiment

```{r}

# To visualize the emotional engagement experiment
SamplesV2=read.csv("SamplesV2.csv")

ggplot(subset(SamplesV2, Task == "SocialEngagement"), aes(x=TrialTime, y=PupilSize, color = ParticipantGender)) + 
  geom_smooth() + facet_grid(~ActorGender) + xlim(0,6000)

ggplot(subset(SamplesV2, Task == "SocialEngagement"), aes(x=TrialTime, y=PupilSize, color = Directionality)) + 
  geom_smooth() + facet_grid(~Ostension) + xlim(0,6000)

# To read fixation data
FixationV2 = read.csv("FixationsV2.csv")

# Subsetting the data for the Social engagement task
SocialData = subset(FixationV2, Task == "SocialEngagement")

set.seed(1) # For reproducibility

# To create folds
data <- fold(SocialData, k = 3,
             cat_col = 'Directionality', 'Ostension',
             id_col = 'ParticipantID') %>% 
  arrange(.folds)

# To specify models
mixed_models <- c("PupilSize ~ Ostension * Directionality + (1+Ostension * Directionality|ParticipantID)",
                  "PupilSize ~ Ostension + Directionality + (1+ Ostension + Directionality|ParticipantID)",
                  "PupilSize ~ Ostension + Directionality + (1|ParticipantID)")

# To crossvalidate
CV1 <- cross_validate(data, mixed_models, folds_col = '.folds', family='gaussian', REML = FALSE)
CV1

# To create models
Socialmodel=lmer(PupilSize ~ Ostension*Directionality + (1+Ostension*Directionality|ParticipantID), SocialData)
summary(Socialmodel)

Socialmodel2=lmer(PupilSize ~ Ostension+Directionality + (1+Ostension+Directionality|ParticipantID), SocialData)
summary(Socialmodel2)

Socialmodel3=lmer(PupilSize ~ Ostension +Directionality + (1|ParticipantID), SocialData)
summary(Socialmodel3)